---
title: "Longitudinal COVID Risk/Reward Behaviors & Mental Health Modeling"
subtitle: "This project aims to examine longitudinal changes in risk- and reward-related behaviors and decision-making among a general community sample over the first year following the initial COVID-19 lock-down in the United States, which began in March 2020. The focus is to understand how these behaviors evolved during the pandemic and to identify the factors influencing these trajectories. This study was conducted by the <a href='https://www.mcleanhospital.org/profile/poornima-kumar'>Computational Psychopathology Laboratory</a> at McLean Hospital & Harvard Medical School."
format:
  lumo-html: 
    logo: "Lab Logo_Transparent.svg" # Optional. Path to a logo displayed above the title
    github-repo: "https://www.github.com/adrian-a-medina/COVID-MultilevelModeling"
    primary-color: "#d62993"
    self-contained: true
    is-particlejs-enabled: true # Optional: display interactive particles in the document header
author: Adrian Medina
date: last-modified
---

## Overview

[**Study Design**]{.underline}**:\
**The study spans from May 2020 to February 2021, encompassing seven sessions including the baseline. Follow-up assessments were conducted at two weeks, one month, six weeks, two months, ten weeks, and three months post-baseline. This design allows for detailed tracking of changes over a crucial period of adjustment to pandemic-related disruptions.

[**Data Collection**]{.underline}**:\
**Data were collected on a variety of domains, including:

-   ***Risky Behaviors***: As characterized by the Centers for Disease Control and Prevention (CDC).
-   ***Risk/Reward Appraisals***: Assessment of individuals’ perceptions and evaluations of risky situations versus potential gains
-   ***Clinical Measures***: Focused primarily on mental health, with a few variables related to physical health.
-   ***Coping & Support Measures***: Insights into how individuals cope with stress and their available support systems.
-   ***Psychometric Measures***: Standardized tests to measure psychological variables, offering a window into the psychological state of participants.

[**Analytic Approach**]{.underline}**:\
**The primary analytic strategy involves using multilevel modeling to:

-   **Determine the best-fitting models** for describing the trajectories of risk/reward behavior variables.
-   **Incorporate clinical, psychometric, coping, and support measures** to enrich our understanding of the factors influencing risk and reward inclinations or aversions during this unprecedented period.

[**Goals**]{.underline}**:\
**The primary analytic strategy involves using multilevel modeling to:

-   **Identify key patterns and changes** in risk-taking and reward-seeking behaviors across the studied time frame.
-   **Explore the impact of psychological and social factors** on these behaviors to better understand the mental health implications of the pandemic.
-   **Develop predictive insights** that can inform future public health strategies and interventions in similar crises.

## Data Frame Initialization

Set up the R environment by configuring the CRAN repository, installing essential packages, and setting base paths.

```{r Package Installation, warning=F, message=F}
#| code-fold: false
# Set CRAN repository for consistent package installation
options(repos = c(CRAN = "http://cran.rstudio.com/"))

if (!require(pacman)) install.packages("pacman")
library(pacman) # <1>

# Use p_load function to install (if necessary) and load packages
p_load(psych, ggplot2, lme4, lmerTest, nlme, dplyr, performance, interactions, sampling, tidyr,
       tidyverse, kableExtra, broom.mixed, gridExtra, sjPlot, ggridges, PupillometryR, 
       patchwork)

# Define base path for streamlined access/replication
base_path <- "~/Dropbox (Partners HealthCare)/Stress_COVID_Decision_making/Analyses/Risk_Behavior/MultilevelModeling"
survey_path <- "~/Dropbox (Partners HealthCare)/Stress_COVID_Decision_making/Data/scored_survey_data/final_data"

```

1.  this package provides efficient package management if using multiple packages within the same file!

The source dataset is loaded and time values are adjusted from 1-7 to 0-6. Initialize unified columns for behavior, risk, and reward variables.

```{r Loading Source Dataset & Data Frame Preparation, message=FALSE, warning=FALSE}
# Set working directory
setwd(base_path)

# Read in source dataset
covid_long <- read.csv("covid_long.csv")

# Recode time from values of 1-7 to 0-6
covid_long$time <- covid_long$Index1 - 1

# Define the behavior variable names
beh_variable_names <- c("L1_mail", "HM26_plane", "L2_takeout", "L4_tennis", "LM7_walk_others", 
                    "LM8_golf", "MOD16_bbq", "HM24_eat_rest_in", "LM9_stay_hotel",
                    "LM11_library", "LM12_eat_rest_out", "LM14_playground", "H33_going_movies",
                    "L5_camping", "MOD17_beach", "MOD18_mall", "LM6_grocery", 
                    "MOD20_work_office", "HM28_play_football", "MOD21_pool", "H37_bar", 
                    "MOD22_visit_relatives", "LM13_walk_downtown", "HM23_hair_salon", 
                    "HM25_wedding", "L3_pump_gas", "HM27_play_basketball", 
                    "MOD15_dinner_friend", "H36_attend_religious", "HM29_shake_hands", 
                    "H30_buffet", "H31_gym", "H32_amusement_park", "LM10_doc_office", 
                    "H34_concert", "H35_going_sports", "MOD19_kids_school")

# Create a new '_unified' column (to organize behavior data in non-iterative manner) for each behavior variable
for (var_name in beh_variable_names) {
  covid_long[paste0(var_name, "_unified")] <- NA
}

# Define the base risk variable names
risk_variable_names <- c("L1Y_mail_risk", "HM26Y_plane_risk", "L2Y_takeout_risk", 
                         "L4Y_tennis_risk", "LM7Y_walk_others_risk", "LM8Y_golf_risk", 
                         "MOD16Y_bbq_risk", "HM24Y_eat_rest_in_risk", "LM9Y_stay_hotel_risk", 
                         "LM11Y_library_risk", "LM12Y_eat_rest_out_risk", 
                         "LM14Y_playground_risk", "H33Y_going_movies_risk", "L5Y_camping_risk",
                         "MOD17Y_beach_risk", "MOD18Y_mall_risk", "LM6Y_grocery_risk", 
                         "MOD20Y_work_office_risk", "HM28Y_play_football_risk", 
                         "MOD21Y_pool_risk", "H37Y_bar_risk", "MOD22Y_visit_relatives_risk", 
                         "LM13Y_walk_downtown_risk", "HM23Y_hair_salon_risk", 
                         "HM25Y_wedding_risk", "L3Y_pump_gas_risk", 
                         "HM27Y_play_basketball_risk", "MOD15Y_dinner_friend_risk", 
                         "H36Y_attend_religious_risk", "HM29Y_shake_hands_risk", 
                         "H30Y_buffet_risk", "H31Y_gym_risk", "H32Y_amusement_park_risk", 
                         "LM10Y_doc_office_risk", "H34Y_concert_risk", "H35Y_going_sports_risk"
                         , "MOD19Y_kids_school_risk", "L1N_mail_risk", "HM26N_plane_risk", 
                         "L2N_takeout_risk", "L4N_tennis_risk", "LM7N_walk_others_risk", 
                         "LM8N_golf_risk", "MOD16N_bbq_risk", "HM24N_eat_rest_in_risk", 
                         "LM9N_stay_hotel_risk", "LM11N_library_risk", 
                         "LM12N_eat_rest_out_risk", "LM14N_playground_risk", 
                         "H33N_going_movies_risk", "L5N_camping_risk", "MOD17N_beach_risk", 
                         "MOD18N_mall_risk", "LM6N_grocery_risk", "MOD20N_work_office_risk", 
                         "HM28N_play_football_risk", "MOD21N_pool_risk", "H37N_bar_risk", 
                         "MOD22N_visit_relatives_risk", "LM13N_walk_downtown_risk", 
                         "HM23N_hair_salon_risk", "HM25N_wedding_risk", "L3N_pump_gas_risk", 
                         "HM27N_play_basketball_risk", "MOD15N_dinner_friend_risk", 
                         "H36N_attend_religious_risk", "HM29N_shake_hands_risk", 
                         "H30N_buffet_risk", "H31N_gym_risk", "H32N_amusement_park_risk", 
                         "LM10N_doc_office_risk", "H34N_concert_risk", "H35N_going_sports_risk"
                         , "MOD19N_kids_school_risk")

# Create a new '_unified' column (to organize risk data in non-iterative manner) for each behavior variable
for (var_name in risk_variable_names) {
  covid_long[paste0(var_name, "_unified")] <- NA
}

# Define the base reward variable names
rew_variable_names <- c("L1Y_mail_rew", "HM26Y_plane_rew", "L2Y_takeout_rew", "L4Y_tennis_rew",
                        "LM7Y_walk_others_rew", "LM8Y_golf_rew", "MOD16Y_bbq_rew", 
                        "HM24Y_eat_rest_in_rew",  "LM9Y_stay_hotel_rew", "LM11Y_library_rew", 
                        "LM12Y_eat_rest_out_rew", "LM14Y_playground_rew", 
                        "H33Y_going_movies_rew", "L5Y_camping_rew", "MOD17Y_beach_rew", 
                        "MOD18Y_mall_rew", "LM6Y_grocery_rew", "MOD20Y_work_office_rew", 
                        "HM28Y_play_football_rew", "MOD21Y_pool_rew", "H37Y_bar_rew", 
                        "MOD22Y_visit_relatives_rew", "LM13Y_walk_downtown_rew", 
                        "HM23Y_hair_salon_rew", "HM25Y_wedding_rew", "L3Y_pump_gas_rew", 
                        "HM27Y_play_basketball_rew", "MOD15Y_dinner_friend_rew", 
                        "H36Y_attend_religious_rew", "HM29Y_shake_hands_rew", "H30Y_buffet_rew"
                        , "H31Y_gym_rew", "H32Y_amusement_park_rew", "LM10Y_doc_office_rew", 
                        "H34Y_concert_rew", "H35Y_going_sports_rew", "MOD19Y_kids_school_rew", 
                        "L1N_mail_rew", "HM26N_plane_rew", "L2N_takeout_rew", "L4N_tennis_rew",
                        "LM7N_walk_others_rew", "LM8N_golf_rew", "MOD16N_bbq_rew", 
                        "HM24N_eat_rest_in_rew", "LM9N_stay_hotel_rew", "LM11N_library_rew", 
                        "LM12N_eat_rest_out_rew", "LM14N_playground_rew", 
                        "H33N_going_movies_rew", "L5N_camping_rew", "MOD17N_beach_rew", 
                        "MOD18N_mall_rew", "LM6N_grocery_rew", "MOD20N_work_office_rew", 
                        "HM28N_play_football_rew", "MOD21N_pool_rew", "H37N_bar_rew", 
                        "MOD22N_visit_relatives_rew", "LM13N_walk_downtown_rew", 
                        "HM23N_hair_salon_rew", "HM25N_wedding_rew", "L3N_pump_gas_rew", 
                        "HM27N_play_basketball_rew", "MOD15N_dinner_friend_rew", 
                        "H36N_attend_religious_rew", "HM29N_shake_hands_rew", "H30N_buffet_rew"
                        , "H31N_gym_rew", "H32N_amusement_park_rew", "LM10N_doc_office_rew", 
                        "H34N_concert_rew", "H35N_going_sports_rew", "MOD19N_kids_school_rew")

# Create a new '_unified' column (to organize reward data in non-iterative manner) for each behavior variable
for (var_name in rew_variable_names) {
  covid_long[paste0(var_name, "_unified")] <- NA
}

```

The code below is meant to search through the source dataset 'covid_long' to determine whether or not each of the behavior, risk, and reward variables contain their longitudinal counterparts (based on the consistent naming scheme already included in the source dataset). This was done to ensure all variables were named correctly, thus ensuring they be included in modeling. **The output for each check should be 'character(0)'**.

```{r Variable Nomenclature Inspection, message=FALSE, warning=FALSE}
# Define the naming scheme for follow-up sessions
follow_up_suffixes <- c("", "_two_week", "_monthly", "_six_week", "_sec_monthly", "_ten_week", "_third_monthly")

# Create a list of all expected columns based on the naming scheme
beh_expected_columns <- unlist(lapply(beh_variable_names, function(var) {
  paste0(var, follow_up_suffixes)
}))

# Check which expected behavior columns are missing in the data frame
beh_missing_columns <- setdiff(beh_expected_columns, names(covid_long))

# Output the missing behavior columns (if any)
print(beh_missing_columns)

# Create a list of all expected risk columns based on the naming scheme
risk_expected_columns <- unlist(lapply(risk_variable_names, function(var) {
  paste0(var, follow_up_suffixes)
}))

# Check which expected risk columns are missing in the data frame
risk_missing_columns <- setdiff(risk_expected_columns, names(covid_long))

# Output the missing risk columns (if any)
print(risk_missing_columns)

# Create a list of all expected reward columns based on the naming scheme
rew_expected_columns <- unlist(lapply(rew_variable_names, function(var) {
  paste0(var, follow_up_suffixes)
}))

# Check which expected reward columns are missing in the data frame
rew_missing_columns <- setdiff(rew_expected_columns, names(covid_long))

# Output the missing reward columns (if any)
print(rew_missing_columns)

```

Filter out subjects with completely missing data across all unified variables, recode 'NA' values to '2' in behavior variables, and populate unified columns according to specific time points, ensuring each column accurately reflects the data for each session.

```{r Filtering Empty Subjects & Recoding Remaining Empty Cells, results='hide', message=FALSE, warning=FALSE}
# Generate unified variable names
beh_unified_vars <- paste0(beh_variable_names, "_unified")
risk_unified_vars <- paste0(risk_variable_names, "_unified")
rew_unified_vars <- paste0(rew_variable_names, "_unified")

# Combine all unified variable names
all_unified_vars <- c(beh_unified_vars, risk_unified_vars, rew_unified_vars)

# Combine all expected columns
all_expected_columns <- c(beh_expected_columns, risk_expected_columns, rew_expected_columns)

# Create the subset dataframe
covid_long_analytic <- covid_long %>%
  select(record_id, time, baseline_date_complete, all_of(c(all_expected_columns, all_unified_vars)))

# Create complete expected columns per variable type
beh_all_columns <- c(beh_expected_columns, beh_unified_vars)
risk_all_columns <- c(risk_expected_columns, risk_unified_vars)
rew_all_columns <- c(rew_expected_columns, rew_unified_vars)
all_columns <- c(all_expected_columns, all_unified_vars)

# Filter out rows where all entries in 'all_columns' are NA
covid_long_filtered <- covid_long_analytic %>%
  filter(rowSums(!is.na(select(., all_of(all_columns)))) > 0)  # Tested using different filter variables, all of which yielded the same amount of subjects + iterations, so kept the most comprehensive option

# Count NA values in each column of the filtered data frame
na_counts <- colSums(is.na(covid_long_filtered))

# Recode NA values to 2 in specified behavior columns using explicit dplyr namespace
covid_long_filtered <- dplyr::mutate(
  covid_long_filtered,
  dplyr::across(dplyr::all_of(beh_expected_columns), ~ dplyr::if_else(is.na(.), 2, .))
)

# Double-check if there are still NA values in these columns
sum_na <- invisible(sapply(covid_long_filtered[beh_expected_columns], function(x) sum(is.na(x))))
print(sum_na)  # This will show the count of NA values per column after the replacement

```

```{r Analytic Variable Coalescence, message=FALSE, warning=FALSE}
#| code-fold: false  
# Explicitly populate the unified behavior columns based on 'time' value
for (var in beh_variable_names) {
  for (i in 0:6) {
    covid_long_filtered <- dplyr::mutate(
      covid_long_filtered,
      !!paste0(var, "_unified") := dplyr::if_else(
        time == i,
        covid_long_filtered[[paste0(var, follow_up_suffixes[i + 1])]],
        covid_long_filtered[[paste0(var, "_unified")]],
        missing = NA
      )
    )
  }
}

# Explicitly populate the unified risk columns based on 'time' value
for (var in risk_variable_names) {
  for (i in 0:6) {
    covid_long_filtered <- dplyr::mutate(
      covid_long_filtered,
      !!paste0(var, "_unified") := dplyr::if_else(
        time == i, 
        covid_long_filtered[[paste0(var, follow_up_suffixes[i + 1])]],
        covid_long_filtered[[paste0(var, "_unified")]],
        missing = NA
      )
    )
  }
}

# Explicitly populate the unified reward columns based on 'time' value
for (var in rew_variable_names) {
  for (i in 0:6) {
    covid_long_filtered <- dplyr::mutate(
      covid_long_filtered,
      !!paste0(var, "_unified") := dplyr::if_else(
        time == i,
        covid_long_filtered[[paste0(var, follow_up_suffixes[i + 1])]],
        covid_long_filtered[[paste0(var, "_unified")]],
        missing = NA
      )
    )
  }
}

```

## Behavior Data: Wrangling & Transformations

Analyzes behavioral responses by filtering subjects with uniform responses and calculating counts of affirmative and negative responses. It summarizes these counts to derive total response metrics for each subject and time point, highlighting behavioral patterns.

```{r Behavior Response Calculation, message=FALSE, warning=FALSE}
# Create the behavior subset data frame
covid_behavior_filtered <- covid_long_filtered %>%
  select(record_id, time, baseline_date_complete, all_of(c(beh_unified_vars)))

# Filter out empty rows of subject data (e.g., '2' in all behavioral variables)
covid_behavior_filtered <- covid_behavior_filtered %>%
  # Add a helper column that checks if all values in specified columns are '2'
  mutate(all_twos = rowSums(across(all_of(beh_unified_vars)) == 2) == length(beh_unified_vars)) %>%
  # Filter out rows where the helper column is TRUE
  filter(!all_twos) %>%
  # Optionally remove the helper column if it's no longer needed
  select(-all_twos)

# Count only '0' values (yes) for each row across selected variables, excluding 'record_id' and 'time'
covid_behavior_filtered$yes_counts <- rowSums(covid_behavior_filtered[, -c(1, 2)] == 0, na.rm = TRUE)

# Count only '1' values (no) for each row across selected variables, excluding 'record_id', 'time', and 'yes_counts'
covid_behavior_filtered$no_counts <- rowSums(covid_behavior_filtered[, -c(1, 2, 40)] == 1, na.rm = TRUE)

# Sum the 'yes_counts' and 'no_counts' to get the total response counts
covid_behavior_filtered$response_counts <- covid_behavior_filtered$yes_counts + covid_behavior_filtered$no_counts

```

## Risk Data: Wrangling & Transformations

Processes risk-related data by excluding subjects with entirely missing risk variables. It calculates non-missing risk sums and counts to compute average risk scores, both total and adjusted for actual data availability, to assess risk profiles longitudinally.

```{r Longitudinal Risk Calculation, message=FALSE, warning=FALSE}
# Create the risk subset data frame
covid_risk_filtered <- covid_long_filtered %>%
  select(record_id, time, baseline_date_complete, all_of(c(risk_unified_vars)))

# Filter out empty rows of subject data (e.g., 'NA' in all risk variables)
covid_risk_filtered <- covid_risk_filtered %>%
  # Add a helper column that checks if all values in specified columns are NA
  mutate(all_na = rowSums(is.na(across(all_of(risk_unified_vars)))) == length(risk_unified_vars)) %>%
  # Filter out rows where the helper column is TRUE
  filter(!all_na) %>%
  # Optionally remove the helper column if it's no longer needed
  select(-all_na)

# Create 'sum_risks' and 'num_risks' columns by summing all risk-related columns for each row, ignoring NA values
covid_risk_filtered$sum_risks <- rowSums(covid_risk_filtered[risk_unified_vars], na.rm = TRUE)
covid_risk_filtered$num_risks <- rowSums(!is.na(covid_risk_filtered[risk_unified_vars]))

# Create 'avg_risk' column for risk variables by dividing 'sum_risks' by 'num_risks'
covid_risk_filtered$avg_risk <- covid_risk_filtered$sum_risks / covid_risk_filtered$num_risks

```

## Reward Data: Wrangling & Transformations

Processes reward-related data by isolating subjects with complete data and computing sums and counts of non-missing reward entries. It derives average reward scores, both overall and adjusted based on data presence, to analyze reward dynamics across time points. The section concludes by merging the refined reward data with previously processed behavioral and risk data to form a comprehensive dataset for further analysis.

```{r Longitudinal Reward Calculation, message=FALSE, warning=FALSE}
# Create the reward subset data frame
covid_rew_filtered <- covid_long_filtered %>%
  select(record_id, time, baseline_date_complete, all_of(c(rew_unified_vars)))

# Filter out empty rows of subject data (e.g., 'NA' in all reward variables)
covid_rew_filtered <- covid_rew_filtered %>%
  # Add a helper column that checks if all values in specified columns are NA
  mutate(all_na = rowSums(is.na(across(all_of(rew_unified_vars)))) == length(rew_unified_vars)) %>%
  # Filter out rows where the helper column is TRUE
  filter(!all_na) %>%
  # Optionally remove the helper column if it's no longer needed
  select(-all_na)

# Create 'sum_rew' and 'num_rew' columns by summing all reward-related columns for each row, ignoring NA values
covid_rew_filtered$sum_rew <- rowSums(covid_rew_filtered[rew_unified_vars], na.rm = TRUE)
covid_rew_filtered$num_rew <- rowSums(!is.na(covid_rew_filtered[rew_unified_vars]))

# Create 'avg_rew_adj' column for reward variables by dividing 'sum_rew' by 'num_rew'
covid_rew_filtered$avg_rew <- covid_rew_filtered$sum_rew / covid_rew_filtered$num_rew

# Merge covid_behavior_filtered with covid_risk_filtered
covid_long_intermediate <- dplyr::left_join(covid_behavior_filtered, covid_risk_filtered, by = c("record_id", "time"))

# Merge the intermediate result with covid_rew_filtered
covid_long_final <- dplyr::left_join(covid_long_intermediate, covid_rew_filtered, by = c("record_id", "time"))

```

## Risk & Reward Data: Stratification & Categorization

Categorizes risk and reward variables into 'Yes' and 'No' groups and then further stratifies them into 'Low', 'Moderate', and 'High' risk categories based on predefined item numbers. Computes the sum and average scores for each group by risk category, enabling detailed analysis of responses within the stratified groups.

```{r Stratifying Variables, message=FALSE, warning=FALSE}
# Split the risk variables into those containing 'Y' and those containing 'N'
risk_Y_unified_vars <- risk_unified_vars[grep("\\dY_", risk_unified_vars)]
risk_N_unified_vars <- risk_unified_vars[grep("\\dN_", risk_unified_vars)]

# Split the reward variables into those containing 'Y' and those containing 'N'
rew_Y_unified_vars <- rew_unified_vars[grep("\\dY_", rew_unified_vars)]
rew_N_unified_vars <- rew_unified_vars[grep("\\dN_", rew_unified_vars)]

# Calculating sum scores for 'yes' and 'no' responses for risk variables
covid_long_final <- covid_long_final %>%
  mutate(
    sum_risk_Y = rowSums(select(., all_of(risk_Y_unified_vars)), na.rm = TRUE),
    sum_risk_N = rowSums(select(., all_of(risk_N_unified_vars)), na.rm = TRUE),
    num_risk_Y = rowSums(!is.na(select(., all_of(risk_Y_unified_vars)))),
    num_risk_N = rowSums(!is.na(select(., all_of(risk_N_unified_vars)))),
    avg_risk_Y = sum_risk_Y / num_risk_Y,
    avg_risk_N = sum_risk_N / num_risk_N
  )

# Calculating sum scores for 'yes' and 'no' responses for reward variables
covid_long_final <- covid_long_final %>%
  mutate(
    sum_rew_Y = rowSums(select(., all_of(rew_Y_unified_vars)), na.rm = TRUE),
    sum_rew_N = rowSums(select(., all_of(rew_N_unified_vars)), na.rm = TRUE),
    num_rew_Y = rowSums(!is.na(select(., all_of(rew_Y_unified_vars)))),
    num_rew_N = rowSums(!is.na(select(., all_of(rew_N_unified_vars)))),
    avg_rew_Y = sum_rew_Y / num_rew_Y,
    avg_rew_N = sum_rew_N / num_rew_N
  )

# Extract item numbers from variable names
item_numbers <- as.numeric(gsub("\\D", "", all_unified_vars))

# Classify each variable into a risk category based on item number
risk_categories <- ifelse(item_numbers %in% 1:8, "Low",
                          ifelse(item_numbers %in% 9:22, "Moderate", "High"))

# Combine variable names with their categories
behavior_categories <- data.frame(variable = all_unified_vars, category = risk_categories)

# Calculating sums and averages for risk categories, 'Yes' and 'No' variables
low_risk_vars <- behavior_categories$variable[behavior_categories$category == "Low"]
moderate_risk_vars <- behavior_categories$variable[behavior_categories$category == "Moderate"]
high_risk_vars <- behavior_categories$variable[behavior_categories$category == "High"]
low_risk_Y_vars <- risk_Y_unified_vars[risk_Y_unified_vars %in% low_risk_vars]
low_risk_N_vars <- risk_N_unified_vars[risk_N_unified_vars %in% low_risk_vars]
moderate_risk_Y_vars <- risk_Y_unified_vars[risk_Y_unified_vars %in% moderate_risk_vars]
moderate_risk_N_vars <- risk_N_unified_vars[risk_N_unified_vars %in% moderate_risk_vars]
high_risk_Y_vars <- risk_Y_unified_vars[risk_Y_unified_vars %in% high_risk_vars]
high_risk_N_vars <- risk_N_unified_vars[risk_N_unified_vars %in% high_risk_vars]

# Calculating sums and averages for reward categories, 'Yes' and 'No' variables
low_rew_vars <- behavior_categories$variable[behavior_categories$category == "Low"]
moderate_rew_vars <- behavior_categories$variable[behavior_categories$category == "Moderate"]
high_rew_vars <- behavior_categories$variable[behavior_categories$category == "High"]
low_rew_Y_vars <- rew_Y_unified_vars[rew_Y_unified_vars %in% low_rew_vars]
low_rew_N_vars <- rew_N_unified_vars[rew_N_unified_vars %in% low_rew_vars]
moderate_rew_Y_vars <- rew_Y_unified_vars[rew_Y_unified_vars %in% moderate_rew_vars]
moderate_rew_N_vars <- rew_N_unified_vars[rew_N_unified_vars %in% moderate_rew_vars]
high_rew_Y_vars <- rew_Y_unified_vars[rew_Y_unified_vars %in% high_rew_vars]
high_rew_N_vars <- rew_N_unified_vars[rew_N_unified_vars %in% high_rew_vars]

# Adding risk calculations to the dataframe
covid_long_final <- covid_long_final %>%
  mutate(
    # Low risk calculations
    sum_low_risk_Y = rowSums(select(., all_of(low_risk_Y_vars)), na.rm = TRUE),
    sum_low_risk_N = rowSums(select(., all_of(low_risk_N_vars)), na.rm = TRUE),
    num_low_risk_Y = rowSums(!is.na(select(., all_of(low_risk_Y_vars)))),
    num_low_risk_N = rowSums(!is.na(select(., all_of(low_risk_N_vars)))),
    avg_low_risk_Y = sum_low_risk_Y / num_low_risk_Y,
    avg_low_risk_N = sum_low_risk_N / num_low_risk_N,

    # Moderate risk calculations
    sum_moderate_risk_Y = rowSums(select(., all_of(moderate_risk_Y_vars)), na.rm = TRUE),
    sum_moderate_risk_N = rowSums(select(., all_of(moderate_risk_N_vars)), na.rm = TRUE),
    num_moderate_risk_Y = rowSums(!is.na(select(., all_of(moderate_risk_Y_vars)))),
    num_moderate_risk_N = rowSums(!is.na(select(., all_of(moderate_risk_N_vars)))),
    avg_moderate_risk_Y = sum_moderate_risk_Y / num_moderate_risk_Y,
    avg_moderate_risk_N = sum_moderate_risk_N / num_moderate_risk_N,

    # High risk calculations
    sum_high_risk_Y = rowSums(select(., all_of(high_risk_Y_vars)), na.rm = TRUE),
    sum_high_risk_N = rowSums(select(., all_of(high_risk_N_vars)), na.rm = TRUE),
    num_high_risk_Y = rowSums(!is.na(select(., all_of(high_risk_Y_vars)))),
    num_high_risk_N = rowSums(!is.na(select(., all_of(high_risk_N_vars)))),
    avg_high_risk_Y = sum_high_risk_Y / num_high_risk_Y,
    avg_high_risk_N = sum_high_risk_N / num_high_risk_N
  )

# Adding reward calculations to the dataframe
covid_long_final <- covid_long_final %>%
  mutate(
    # Low reward calculations
    sum_low_rew_Y = rowSums(select(., all_of(low_rew_Y_vars)), na.rm = TRUE),
    sum_low_rew_N = rowSums(select(., all_of(low_rew_N_vars)), na.rm = TRUE),
    num_low_rew_Y = rowSums(!is.na(select(., all_of(low_rew_Y_vars)))),
    num_low_rew_N = rowSums(!is.na(select(., all_of(low_rew_N_vars)))),
    avg_low_rew_Y = sum_low_rew_Y / num_low_rew_Y,
    avg_low_rew_N = sum_low_rew_N / num_low_rew_N,

    # Moderate reward calculations
    sum_moderate_rew_Y = rowSums(select(., all_of(moderate_rew_Y_vars)), na.rm = TRUE),
    sum_moderate_rew_N = rowSums(select(., all_of(moderate_rew_N_vars)), na.rm = TRUE),
    num_moderate_rew_Y = rowSums(!is.na(select(., all_of(moderate_rew_Y_vars)))),
    num_moderate_rew_N = rowSums(!is.na(select(., all_of(moderate_rew_N_vars)))),
    avg_moderate_rew_Y = sum_moderate_rew_Y / num_moderate_rew_Y,
    avg_moderate_rew_N = sum_moderate_rew_N / num_moderate_rew_N,

    # High reward calculations
    sum_high_rew_Y = rowSums(select(., all_of(high_rew_Y_vars)), na.rm = TRUE),
    sum_high_rew_N = rowSums(select(., all_of(high_rew_N_vars)), na.rm = TRUE),
    num_high_rew_Y = rowSums(!is.na(select(., all_of(high_rew_Y_vars)))),
    num_high_rew_N = rowSums(!is.na(select(., all_of(high_rew_N_vars)))),
    avg_high_rew_Y = sum_high_rew_Y / num_high_rew_Y,
    avg_high_rew_N = sum_high_rew_N / num_high_rew_N
  )

```

## Mental Health Data: Wrangling & Transformations

Converts mental health survey data from wide to long format for analytical flexibility. It cleans and summarizes the data, mapping each variable to its respective time points defined by suffixes, calculating the number of iterations and value ranges for each variable. This process involves removing redundant rows and establishing a clear structure to facilitate longitudinal analyses, incorporating a 'time_factor' column to align data points with specific survey phases.

**Please note**: the mental health data requires a slightly different approach, and thus, comes with its own unique transformations as a result of each variable having different frequencies of occurrence in the data collection sequence.

```{r Mental Health Scores Data Preparation, message=FALSE, warning=FALSE}
setwd(survey_path)

# Read in longitudinal mental health questionnaire data, presently in wide format
mentalhealth_survey_data <- read.csv("FINAL_SURVEY_DATA_2024-06-12.csv")

# Extract the column names
column_names <- names(mentalhealth_survey_data)

# Create a list where each base variable name is mapped to its original column names after removing suffixes
base_variable_names <- str_remove_all(column_names, 
                                      pattern = "_baseline|_two_week|_monthly|_six_week|_second_monthly|_ten_week|_third_monthly")

# Create a unique list of base variable names
unique_base_variables <- unique(base_variable_names)

# Create a data frame to store the summary of each variable
variable_summary <- data.frame(variable = unique_base_variables)

# Calculate the number of iterations and value ranges
variable_summary <- variable_summary %>%
  rowwise() %>%
  mutate(
    iterations = length(grep(paste0("^", variable, "(_|$)"), column_names)),
    value_range = {
      cols <- names(mentalhealth_survey_data)[grep(paste0("^", variable, "(_|$)"), column_names)]
      min_val <- min(unlist(mentalhealth_survey_data[cols], use.names = FALSE), na.rm = TRUE)
      max_val <- max(unlist(mentalhealth_survey_data[cols], use.names = FALSE), na.rm = TRUE)
      paste(min_val, max_val, sep = "-")
    }
  )

# Manual edits to the data frame iteration values to account for variables with similar base names
variable_summary <- variable_summary %>%
  mutate(
    iterations = case_when(
      variable == "ami" ~ "7",
      variable == "bis" ~ "4",
      variable == "dsm_anger" ~ "4",
      variable == "dsm_anhedonia" ~ "4",
      variable == "dsm_anxiety" ~ "4",
      variable == "dsm_depression" ~ "4",
      variable == "dsm_dissociation" ~ "4",
      variable == "dsm_dysphoria" ~ "4",
      variable == "dsm_mania" ~ "4",
      variable == "dsm_memory" ~ "4",
      variable == "dsm_personality" ~ "4",
      variable == "dsm_psychosis" ~ "4",
      variable == "dsm_repetition" ~ "4",
      variable == "dsm_sleep" ~ "4",
      variable == "dsm_somatic" ~ "4",
      variable == "dsm_suicidality" ~ "4",
      variable == "dsm_substance" ~ "4",
      variable == "dsm_total" ~ "4",
      variable == "mpss" ~ "4",
      variable == "panas_positive" ~ "1",
      variable == "panas_negative" ~ "1",
      variable == "promis_pain" ~ "2",
      variable == "promis_physical" ~ "2",
      TRUE ~ as.character(iterations)  # Keep existing iterations for other variables
    )
  ) %>%
  filter(variable != "record_id")  # Remove the row where variable is 'record_id'

# Define time suffixes and factors
time_suffixes <- list(
  `7` = c("_baseline", "_two_week", "_monthly", "_six_week", "_second_monthly", "_ten_week", "_third_monthly"),
  `4` = c("_baseline", "_monthly", "_second_monthly", "_third_monthly"),
  `2` = c("_baseline", "_two_week"),
  `1` = c("_baseline")
)

time_factors <- list(
  `7` = c("Baseline", "Two Week Follow-Up", "One Month Follow-Up", "Six Week Follow-Up", "Two Month Follow-Up", "Ten Week Follow-Up", "Three Month Follow-Up"),
  `4` = c("Baseline", "One Month Follow-Up", "Two Month Follow-Up", "Three Month Follow-Up"),
  `2` = c("Baseline", "Two Week Follow-Up"),
  `1` = c("Baseline")
)

# Transforming mentalhealth_survey_data from wide to long format and creating 'time_factor'
mentalhealth_survey_data_long <- mentalhealth_survey_data %>%
  pivot_longer(
    cols = -record_id,  # Assuming 'record_id' is the identifier and should not be pivoted
    names_to = "variable_time",
    values_to = "value"
  ) %>%
  mutate(
    time = case_when(
      str_detect(variable_time, "_baseline") ~ 0,
      str_detect(variable_time, "_two_week") ~ 1,
      str_detect(variable_time, "_monthly") & !str_detect(variable_time, "second_monthly") & !str_detect(variable_time, "third_monthly") ~ 2,
      str_detect(variable_time, "_six_week") ~ 3,
      str_detect(variable_time, "_second_monthly") ~ 4,
      str_detect(variable_time, "_ten_week") ~ 5,
      str_detect(variable_time, "_third_monthly") ~ 6,
      TRUE ~ as.integer(NA)  # Handling unexpected cases
    ),
    variable = str_remove(variable_time, "_baseline|_two_week|_monthly|_six_week|_second_monthly|_ten_week|_third_monthly"),
    time_factor = factor(
      case_when(
        time == 0 ~ "Baseline",
        time == 1 ~ "Two Week Follow-Up",
        time == 2 ~ "One Month Follow-Up",
        time == 3 ~ "Six Week Follow-Up",
        time == 4 ~ "Two Month Follow-Up",
        time == 5 ~ "Ten Week Follow-Up",
        time == 6 ~ "Three Month Follow-Up",
        TRUE ~ NA_character_  # Handles any unexpected cases
      ),
      levels = c("Baseline", "Two Week Follow-Up", "One Month Follow-Up", "Six Week Follow-Up", "Two Month Follow-Up", "Ten Week Follow-Up", "Three Month Follow-Up")
    )
  ) %>%
  select(record_id, time, time_factor, variable, value)  # Reorder and select only necessary columns

# Omit specific time points for DSM variables
dsm_vars <- c("dsm_anger", "dsm_anhedonia", "dsm_anxiety", "dsm_depression", "dsm_dissociation"
              , "dsm_dysphoria", "dsm_mania", "dsm_memory", "dsm_personality", "dsm_psychosis",
              "dsm_repetition", "dsm_sleep", "dsm_somatic", "dsm_suicidality", "dsm_substance",
              "dsm_total")

omit_times <- c("Two Week Follow-Up", "Six Week Follow-Up", "Ten Week Follow-Up")

# Filter out unwanted time points for DSM variables
mentalhealth_survey_data_long <- mentalhealth_survey_data_long %>%
  filter(!(variable %in% dsm_vars & time_factor %in% omit_times))

# Keep specific time points for PROMIS variables
promis_vars <- c("promis_pain", "promis_physical")
keep_promis_times <- c("Baseline", "Two Week Follow-Up")

# Filter and keep specific time points for PROMIS variables
mentalhealth_survey_data_long <- mentalhealth_survey_data_long %>%
  filter(!(variable %in% promis_vars) | (variable %in% promis_vars & time_factor %in% keep_promis_times))

# Keep specific time points for PANAS variables
panas_vars <- c("panas_positive", "panas_negative")
keep_panas_times <- "Baseline"

# Filter and keep specific time points for PANAS variables
mentalhealth_survey_data_long <- mentalhealth_survey_data_long %>%
  filter(!(variable %in% panas_vars) | (variable %in% panas_vars & time_factor == keep_panas_times))

# Print the updated data frame to verify that variables were properly transformed
print(mentalhealth_survey_data_long)

```

## Descriptive Statistics & Visualizations

Please use the data frame '**covid_long_final**' for any descriptive statistics calculations or visualizations pertaining to behavior, risk, &/or reward data. **Note**: **These data frames are already in long format**.

Extracts descriptive statistics for behavior, risk, reward, and mental health data across different time points. Outputs are then converted into a consolidated data frame, reformatted for improved readability, and displayed as a multi-tiered HTML table with headers representing each time point.

```{r Calculating & Tabling Descriptives for Behavior, Risk, and Reward Data, message=FALSE, warning=FALSE}
# Reorder columns in final data frame to verify baseline completion dates match
covid_long_final <- covid_long_final %>%
  select(record_id, time, baseline_date_complete, baseline_date_complete.x, baseline_date_complete.y, everything())

# Following verification, remove the duplicate columns
covid_long_final <- covid_long_final %>%
  select(-baseline_date_complete.x, -baseline_date_complete.y)

# Add new column assigning group label based on baseline completion date and ensure it's a factor
covid_long_final <- covid_long_final %>%
  mutate(baseline_date_complete = mdy(baseline_date_complete),  # Convert to Date format if not already
         covid_group = case_when(
           baseline_date_complete >= mdy("05/01/2020") & baseline_date_complete <= mdy("11/30/2020") ~ "first_wave",
           baseline_date_complete >= mdy("12/01/2020") & baseline_date_complete <= mdy("2/28/2021") ~ "second_wave",
           TRUE ~ NA_character_  # for dates outside the range or NA
         ),
         covid_group = factor(covid_group, levels = c("first_wave", "second_wave"))) %>%
  relocate(covid_group, .after = baseline_date_complete)  # Move covid_group right after baseline_date_complete

# Function to convert describeBy output to data frame
describe_to_df <- function(describe_obj) {
  bind_rows(lapply(describe_obj, as.data.frame))
}

# Generate describeBy outputs
describe_sum_risk_Y <- describeBy(covid_long_final$sum_risk_Y, group = covid_long_final$time)
describe_sum_risk_N <- describeBy(covid_long_final$sum_risk_N, group = covid_long_final$time)
describe_avg_risk_Y <- describeBy(covid_long_final$avg_risk_Y, group = covid_long_final$time)
describe_avg_risk_N <- describeBy(covid_long_final$avg_risk_N, group = covid_long_final$time)
describe_sum_low_risk_Y <- describeBy(covid_long_final$sum_low_risk_Y, group = covid_long_final$time)
describe_sum_low_risk_N <- describeBy(covid_long_final$sum_low_risk_N, group = covid_long_final$time)
describe_avg_low_risk_Y <- describeBy(covid_long_final$avg_low_risk_Y, group = covid_long_final$time)
describe_avg_low_risk_N <- describeBy(covid_long_final$avg_low_risk_N, group = covid_long_final$time)
describe_sum_moderate_risk_Y <- describeBy(covid_long_final$sum_moderate_risk_Y, group = covid_long_final$time)
describe_sum_moderate_risk_N <- describeBy(covid_long_final$sum_moderate_risk_N, group = covid_long_final$time)
describe_avg_moderate_risk_Y <- describeBy(covid_long_final$avg_moderate_risk_Y, group = covid_long_final$time)
describe_avg_moderate_risk_N <- describeBy(covid_long_final$avg_moderate_risk_N, group = covid_long_final$time)
describe_sum_high_risk_Y <- describeBy(covid_long_final$sum_high_risk_Y, group = covid_long_final$time)
describe_sum_high_risk_N <- describeBy(covid_long_final$sum_high_risk_N, group = covid_long_final$time)
describe_avg_high_risk_Y <- describeBy(covid_long_final$avg_high_risk_Y, group = covid_long_final$time)
describe_avg_high_risk_N <- describeBy(covid_long_final$avg_high_risk_N, group = covid_long_final$time)
describe_sum_rew_Y <- describeBy(covid_long_final$sum_rew_Y, group = covid_long_final$time)
describe_sum_rew_N <- describeBy(covid_long_final$sum_rew_N, group = covid_long_final$time)
describe_avg_rew_Y <- describeBy(covid_long_final$avg_rew_Y, group = covid_long_final$time)
describe_avg_rew_N <- describeBy(covid_long_final$avg_rew_N, group = covid_long_final$time)
describe_sum_low_rew_Y <- describeBy(covid_long_final$sum_low_rew_Y, group = covid_long_final$time)
describe_sum_low_rew_N <- describeBy(covid_long_final$sum_low_rew_N, group = covid_long_final$time)
describe_avg_low_rew_Y <- describeBy(covid_long_final$avg_low_rew_Y, group = covid_long_final$time)
describe_avg_low_rew_N <- describeBy(covid_long_final$avg_low_rew_N, group = covid_long_final$time)
describe_sum_moderate_rew_Y <- describeBy(covid_long_final$sum_moderate_rew_Y, group = covid_long_final$time)
describe_sum_moderate_rew_N <- describeBy(covid_long_final$sum_moderate_rew_N, group = covid_long_final$time)
describe_avg_moderate_rew_Y <- describeBy(covid_long_final$avg_moderate_rew_Y, group = covid_long_final$time)
describe_avg_moderate_rew_N <- describeBy(covid_long_final$avg_moderate_rew_N, group = covid_long_final$time)
describe_sum_high_rew_Y <- describeBy(covid_long_final$sum_high_rew_Y, group = covid_long_final$time)
describe_sum_high_rew_N <- describeBy(covid_long_final$sum_high_rew_N, group = covid_long_final$time)
describe_avg_high_rew_Y <- describeBy(covid_long_final$avg_high_rew_Y, group = covid_long_final$time)
describe_avg_high_rew_N <- describeBy(covid_long_final$avg_high_rew_N, group = covid_long_final$time)

# Convert each describeBy output to data frame
df_sum_risk_Y <- describe_to_df(describe_sum_risk_Y)
df_sum_risk_N <- describe_to_df(describe_sum_risk_N)
df_avg_risk_Y <- describe_to_df(describe_avg_risk_Y)
df_avg_risk_N <- describe_to_df(describe_avg_risk_N)
df_sum_low_risk_Y <- describe_to_df(describe_sum_low_risk_Y)
df_sum_low_risk_N <- describe_to_df(describe_sum_low_risk_N)
df_avg_low_risk_Y <- describe_to_df(describe_avg_low_risk_Y)
df_avg_low_risk_N <- describe_to_df(describe_avg_low_risk_N)
df_sum_moderate_risk_Y <- describe_to_df(describe_sum_moderate_risk_Y)
df_sum_moderate_risk_N <- describe_to_df(describe_sum_moderate_risk_N)
df_avg_moderate_risk_Y <- describe_to_df(describe_avg_moderate_risk_Y)
df_avg_moderate_risk_N <- describe_to_df(describe_avg_moderate_risk_N)
df_sum_high_risk_Y <- describe_to_df(describe_sum_high_risk_Y)
df_sum_high_risk_N <- describe_to_df(describe_sum_high_risk_N)
df_avg_high_risk_Y <- describe_to_df(describe_avg_high_risk_Y)
df_avg_high_risk_N <- describe_to_df(describe_avg_high_risk_N)
df_sum_rew_Y <- describe_to_df(describe_sum_rew_Y)
df_sum_rew_N <- describe_to_df(describe_sum_rew_N)
df_avg_rew_Y <- describe_to_df(describe_avg_rew_Y)
df_avg_rew_N <- describe_to_df(describe_avg_rew_N)
df_sum_low_rew_Y <- describe_to_df(describe_sum_low_rew_Y)
df_sum_low_rew_N <- describe_to_df(describe_sum_low_rew_N)
df_avg_low_rew_Y <- describe_to_df(describe_avg_low_rew_Y)
df_avg_low_rew_N <- describe_to_df(describe_avg_low_rew_N)
df_sum_moderate_rew_Y <- describe_to_df(describe_sum_moderate_rew_Y)
df_sum_moderate_rew_N <- describe_to_df(describe_sum_moderate_rew_N)
df_avg_moderate_rew_Y <- describe_to_df(describe_avg_moderate_rew_Y)
df_avg_moderate_rew_N <- describe_to_df(describe_avg_moderate_rew_N)
df_sum_high_rew_Y <- describe_to_df(describe_sum_high_rew_Y)
df_sum_high_rew_N <- describe_to_df(describe_sum_high_rew_N)
df_avg_high_rew_Y <- describe_to_df(describe_avg_high_rew_Y)
df_avg_high_rew_N <- describe_to_df(describe_avg_high_rew_N)

# Combine all data frames into one
combined_df <- bind_rows(
  df_sum_risk_Y %>% mutate(variable = "sum_risk_Y"),
  df_sum_risk_N %>% mutate(variable = "sum_risk_N"),
  df_avg_risk_Y %>% mutate(variable = "avg_risk_Y"),
  df_avg_risk_N %>% mutate(variable = "avg_risk_N"),
  df_sum_low_risk_Y %>% mutate(variable = "sum_low_risk_Y"),
  df_sum_low_risk_N %>% mutate(variable = "sum_low_risk_N"),
  df_avg_low_risk_Y %>% mutate(variable = "avg_low_risk_Y"),
  df_avg_low_risk_N %>% mutate(variable = "avg_low_risk_N"),
  df_sum_moderate_risk_Y %>% mutate(variable = "sum_moderate_risk_Y"),
  df_sum_moderate_risk_N %>% mutate(variable = "sum_moderate_risk_N"),
  df_avg_moderate_risk_Y %>% mutate(variable = "avg_moderate_risk_Y"),
  df_avg_moderate_risk_N %>% mutate(variable = "avg_moderate_risk_N"),
  df_sum_high_risk_Y %>% mutate(variable = "sum_high_risk_Y"),
  df_sum_high_risk_N %>% mutate(variable = "sum_high_risk_N"),
  df_avg_high_risk_Y %>% mutate(variable = "avg_high_risk_Y"),
  df_avg_high_risk_N %>% mutate(variable = "avg_high_risk_N"),
  df_sum_rew_Y %>% mutate(variable = "sum_rew_Y"),
  df_sum_rew_N %>% mutate(variable = "sum_rew_N"),
  df_avg_rew_Y %>% mutate(variable = "avg_rew_Y"),
  df_avg_rew_N %>% mutate(variable = "avg_rew_N"),
  df_sum_low_rew_Y %>% mutate(variable = "sum_low_rew_Y"),
  df_sum_low_rew_N %>% mutate(variable = "sum_low_rew_N"),
  df_avg_low_rew_Y %>% mutate(variable = "avg_low_rew_Y"),
  df_avg_low_rew_N %>% mutate(variable = "avg_low_rew_N"),
  df_sum_moderate_rew_Y %>% mutate(variable = "sum_moderate_rew_Y"),
  df_sum_moderate_rew_N %>% mutate(variable = "sum_moderate_rew_N"),
  df_avg_moderate_rew_Y %>% mutate(variable = "avg_moderate_rew_Y"),
  df_avg_moderate_rew_N %>% mutate(variable = "avg_moderate_rew_N"),
  df_sum_high_rew_Y %>% mutate(variable = "sum_high_rew_Y"),
  df_sum_high_rew_N %>% mutate(variable = "sum_high_rew_N"),
  df_avg_high_rew_Y %>% mutate(variable = "avg_high_rew_Y"),
  df_avg_high_rew_N %>% mutate(variable = "avg_high_rew_N")
)

# Rename 'vars' to 'time'
combined_df <- combined_df %>%
  dplyr::rename(time = vars)

# Recode the 'time' column to have a sequence from 0 to 6 for each set of variables
combined_df <- combined_df %>%
  dplyr::mutate(time = rep(0:6, length.out = n()))

# Spread the combined data frame for a nicer format
final_table <- combined_df %>%
  select(variable, time, n, mean, sd, median, min, max)

# Pivot the data to a wider format with a specific order for statistics
wide_df <- final_table %>%
  pivot_wider(
    names_from = time,  # Assuming 'time' column is correctly set as a factor or numeric already
    values_from = c(n, mean, sd, median, min, max),
    names_sep = "_"  # Creating column names like mean_0, sd_0, etc.
  ) %>%
  select(variable,
         starts_with("n"), starts_with("mean"), starts_with("sd"), starts_with("median"),
         starts_with("min"), starts_with("max"))

# Generate the ordered column names dynamically based on the desired pattern
stats_order <- c("n", "mean", "sd", "median", "min", "max")
time_points <- 0:6  # Assuming time points are from 0 to 6
ordered_column_names <- unlist(lapply(time_points, function(t) paste(stats_order, t, sep = "_")))

# Select columns in the desired order
wide_df <- wide_df %>%
  select(variable, all_of(ordered_column_names))

# Now, strip the time suffixes from the column names for display purposes only
clean_column_names <- rep(stats_order, times = length(time_points))

# Rename the columns for display
names(wide_df)[-1] <- clean_column_names  # Excluding the first column which is 'variable'

# Create the formatted table with specified header spans
formatted_table <- kable(wide_df, "html", escape = FALSE) %>%
  kable_styling(full_width = FALSE, position = "left") %>%
  add_header_above(c(" " = 1, 
                     "Baseline" = length(stats_order), 
                     "Two Week Follow-Up" = length(stats_order), 
                     "One Month Follow-Up" = length(stats_order), 
                     "Six Week Follow-Up" = length(stats_order), 
                     "Two Month Follow-Up" = length(stats_order), 
                     "Ten Week Follow-Up" = length(stats_order), 
                     "Three Month Follow-Up" = length(stats_order))) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  scroll_box(width = "100%", height = "500px")

# Print the formatted table
formatted_table

```

```{r Calculating & Tabling Descriptives for Mental Health Data, message=FALSE, warning=FALSE}
# Map from time factors to numerical values
time_mapping <- c('Baseline' = 0,
                  'Two Week Follow-Up' = 1,
                  'One Month Follow-Up' = 2,
                  'Six Week Follow-Up' = 3,
                  'Two Month Follow-Up' = 4,
                  'Ten Week Follow-Up' = 5,
                  'Three Month Follow-Up' = 6)

# Store results in a list
summary_list <- list()

# Loop over each variable in the variable_summary data frame
for (i in 1:nrow(variable_summary)) {
  variable_name <- variable_summary$variable[i]
  iterations <- as.character(variable_summary$iterations[i])
  
  # Get the appropriate suffixes and time factors for the current number of iterations
  suffixes <- time_suffixes[[iterations]]
  factors <- time_factors[[iterations]]
  
  # Create a data frame to store summaries for the current variable
  variable_data <- list()
  
  # Calculate statistics for each suffix
  for (j in seq_along(suffixes)) {
    full_var_name <- paste0(variable_name, suffixes[j])
    # Check if the column exists in the data, to avoid errors
    if (full_var_name %in% names(mentalhealth_survey_data)) {
      temp_data <- mentalhealth_survey_data %>%
        dplyr::summarise(
          score_mean = mean(.data[[full_var_name]], na.rm = TRUE),
          n = sum(!is.na(.data[[full_var_name]])),  # Sample size excluding NAs
          sem = sd(.data[[full_var_name]], na.rm = TRUE) / sqrt(sum(!is.na(.data[[full_var_name]]))),
          .groups = 'drop'
        ) %>%
        mutate(
          time_factor = factors[j],
          time = time_mapping[[factors[j]]]  # Assign numerical time based on factor
        )
      
      variable_data[[j]] <- temp_data
    }
  }
  
  # Combine all time point data into one data frame for the current variable
  variable_data <- bind_rows(variable_data)
  summary_list[[variable_name]] <- variable_data
}

# Optionally, if you want to save each data frame separately or operate further
for (name in names(summary_list)) {
  assign(paste0("filtered_", name, "_summary"), summary_list[[name]], envir = .GlobalEnv)
}

```

Visual representations are crafted for average risk and reward scores using box plots and density ridge plots, segregated by time factors. This section meticulously prepares the data descriptives, culminating in a series of raincloud plots that highlight temporal variations in the dataset.

```{r Descriptive Visualizations for Behavior, Risk, and Reward Data, message=FALSE, warning=FALSE}
# Prepare the time factor
covid_long_final <- covid_long_final %>%
  mutate(
    time_factor = factor(time, levels = 0:6, labels = c(
      "Baseline", "Two Week Follow-Up", "One Month Follow-Up", 
      "Six Week Follow-Up", "Two Month Follow-Up", "Ten Week Follow-Up", 
      "Three Month Follow-Up"
    ))
  )

# Creating the density ridge plot for average 'yes' risk scores
p1 <- ggplot(covid_long_final, aes(x = avg_risk_Y, y = time_factor, fill = time_factor)) +
  ggridges::geom_density_ridges(alpha = 0.5, jittered_points = TRUE, point_alpha = 0.5, size = 0.25, point_shape = 20, aes(color = time_factor)) +
  labs(x = "Avg 'Yes' Risk Score", y = '') +
  guides(fill = FALSE, color = FALSE) +
  theme_minimal() +
  xlim(0, 100)

# Creating the density ridge plot for average 'no' risk scores
p2 <- ggplot(covid_long_final, aes(x = avg_risk_N, y = time_factor, fill = time_factor)) +
  ggridges::geom_density_ridges(alpha = 0.5, jittered_points = TRUE, point_alpha = 0.5, size = 0.25, point_shape = 20, aes(color = time_factor)) +
  labs(x = "Avg 'No' Risk Score", y = '') +
  guides(fill = FALSE, color = FALSE) +
  theme_minimal() +
  xlim(0, 100)

# Display the density plots
grid.arrange(p1, p2, ncol = 2)

# Creating the density ridge plot for average 'yes' reward scores
p3 <- ggplot(covid_long_final, aes(x = avg_rew_Y, y = time_factor, fill = time_factor)) +
  ggridges::geom_density_ridges(alpha = 0.5, jittered_points = TRUE, point_alpha = 0.5, size = 0.25, point_shape = 20, aes(color = time_factor)) +
  labs(x = "Avg 'Yes' Reward Score", y = '') +
  guides(fill = FALSE, color = FALSE) +
  theme_minimal() +
  xlim(0, 100)

# Creating the density ridge plot for average 'no' reward scores
p4 <- ggplot(covid_long_final, aes(x = avg_rew_N, y = time_factor, fill = time_factor)) +
  ggridges::geom_density_ridges(alpha = 0.5, jittered_points = TRUE, point_alpha = 0.5, size = 0.25, point_shape = 20, aes(color = time_factor)) +
  labs(x = "Avg 'No' Reward Score", y = '') +
  guides(fill = FALSE, color = FALSE) +
  theme_minimal() +
  xlim(0, 100)

# Display the density plots
grid.arrange(p3, p4, ncol = 2)

# Create the summary avg risk 'Y' data frame
filtered_AvgRiskY_summary <- covid_long_final %>%
  group_by(time_factor) %>%
  dplyr::summarise(
    score_mean = mean(avg_risk_Y, na.rm = TRUE),
    n = n(), # Sample size for each group
    sem = sd(avg_risk_Y, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

# Create the summary avg risk 'N' data frame
filtered_AvgRiskN_summary <- covid_long_final %>%
  group_by(time_factor) %>%
  dplyr::summarise(
    score_mean = mean(avg_risk_N, na.rm = TRUE),
    n = n(), # Sample size for each group
    sem = sd(avg_risk_N, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

# Create the summary avg reward 'Y' data frame
filtered_AvgRewY_summary <- covid_long_final %>%
  group_by(time_factor) %>%
  dplyr::summarise(
    score_mean = mean(avg_rew_Y, na.rm = TRUE),
    n = n(), # Sample size for each group
    sem = sd(avg_rew_Y, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

# Create the summary avg reward 'N' data frame
filtered_AvgRewN_summary <- covid_long_final %>%
  group_by(time_factor) %>%
  dplyr::summarise(
    score_mean = mean(avg_rew_N, na.rm = TRUE),
    n = n(), # Sample size for each group
    sem = sd(avg_rew_N, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

# Create a avg 'yes' risk raincloud plot
p5 <- ggplot(covid_long_final, aes(x = time_factor, y = avg_risk_Y, fill = time_factor, color = time_factor)) +
  geom_flat_violin(adjust = 1.5, trim = FALSE, alpha = 0.5, position = position_nudge(x = 0.2, y = 0), colour = NA) +
  geom_point(aes(x = as.numeric(time_factor)-0.25, y = avg_risk_Y, colour = time_factor), position = position_jitter(width = .05), size = .5, shape = 20) +
  geom_boxplot(outlier.shape = NA, alpha = 0.5, width = 0.25, position = position_dodge(width = 0.3), colour = "black") +
  geom_point(data = filtered_AvgRiskY_summary, aes(x = factor(time_factor), y = score_mean), shape = 18, position = position_nudge(x = 0.2)) +
  geom_errorbar(data = filtered_AvgRiskY_summary, aes(x = factor(time_factor), y = score_mean, ymin = score_mean - sem, ymax = score_mean + sem), width = 0.05, position = position_nudge(x = 0.2)) +
  labs(
    title = "Avg 'Yes' Risk Scores by Time Point", 
    y = "Score", 
    x = "Time Point", 
    fill = "Time Point",  # Legend title for fill
    color = "Time Point"  # Legend title for color
  ) +
  theme_minimal() +
  theme(
    legend.position = "right",
    legend.title = element_text(face = "bold"), # Make legend title bold
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels by 45 degrees
  ) +
  ylim(-5, 105)

print(p5)

# Create a avg 'no' risk raincloud plot
p6 <- ggplot(covid_long_final, aes(x = time_factor, y = avg_risk_N, fill = time_factor, color = time_factor)) +
  geom_flat_violin(adjust = 1.5, trim = FALSE, alpha = 0.5, position = position_nudge(x = 0.2, y = 0), colour = NA) +
  geom_point(aes(x = as.numeric(time_factor)-0.25, y = avg_risk_N, colour = time_factor), position = position_jitter(width = .05), size = .5, shape = 20) +
  geom_boxplot(outlier.shape = NA, alpha = 0.5, width = 0.25, position = position_dodge(width = 0.3), colour = "black") +
  geom_point(data = filtered_AvgRiskN_summary, aes(x = factor(time_factor), y = score_mean), shape = 18, position = position_nudge(x = 0.2)) +
  geom_errorbar(data = filtered_AvgRiskN_summary, aes(x = factor(time_factor), y = score_mean, ymin = score_mean - sem, ymax = score_mean + sem), width = 0.05, position = position_nudge(x = 0.2)) +
  labs(
    title = "Avg 'No' Risk Scores by Time Point", 
    y = "Score", 
    x = "Time Point", 
    fill = "Time Point",  # Legend title for fill
    color = "Time Point"  # Legend title for color
  ) +
  theme_minimal() +
  theme(
    legend.position = "right",
    legend.title = element_text(face = "bold"), # Make legend title bold
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels by 45 degrees
  ) +
  ylim(-5, 105)

print(p6)

# Combine raincloud plots and place the legend on the right
combined_plot56 <- p5 + p6 + plot_layout(guides = 'collect') &
  theme(legend.position = 'right')

# Print the combined plot
print(combined_plot56)

# Create a avg 'yes' reward raincloud plot
p7 <- ggplot(covid_long_final, aes(x = time_factor, y = avg_rew_Y, fill = time_factor, color = time_factor)) +
  geom_flat_violin(adjust = 1.5, trim = FALSE, alpha = 0.5, position = position_nudge(x = 0.2, y = 0), colour = NA) +
  geom_point(aes(x = as.numeric(time_factor)-0.25, y = avg_rew_Y, colour = time_factor), position = position_jitter(width = .05), size = .5, shape = 20) +
  geom_boxplot(outlier.shape = NA, alpha = 0.5, width = 0.25, position = position_dodge(width = 0.3), colour = "black") +
  geom_point(data = filtered_AvgRewY_summary, aes(x = factor(time_factor), y = score_mean), shape = 18, position = position_nudge(x = 0.2)) +
  geom_errorbar(data = filtered_AvgRewY_summary, aes(x = factor(time_factor), y = score_mean, ymin = score_mean - sem, ymax = score_mean + sem), width = 0.05, position = position_nudge(x = 0.2)) +
  labs(
    title = "Avg 'Yes' Reward Scores by Time Point", 
    y = "Score", 
    x = "Time Point", 
    fill = "Time Point",  # Legend title for fill
    color = "Time Point"  # Legend title for color
  ) +
  theme_minimal() +
  theme(
    legend.position = "right",
    legend.title = element_text(face = "bold"), # Make legend title bold
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels by 45 degrees
  ) +
  ylim(-5, 105)

print(p7)

# Create a avg 'no' reward raincloud plot
p8 <- ggplot(covid_long_final, aes(x = time_factor, y = avg_rew_N, fill = time_factor, color = time_factor)) +
  geom_flat_violin(adjust = 1.5, trim = FALSE, alpha = 0.5, position = position_nudge(x = 0.2, y = 0), colour = NA) +
  geom_point(aes(x = as.numeric(time_factor)-0.25, y = avg_rew_N, colour = time_factor), position = position_jitter(width = .05), size = .5, shape = 20) +
  geom_boxplot(outlier.shape = NA, alpha = 0.5, width = 0.25, position = position_dodge(width = 0.3), colour = "black") +
  geom_point(data = filtered_AvgRewN_summary, aes(x = factor(time_factor), y = score_mean), shape = 18, position = position_nudge(x = 0.2)) +
  geom_errorbar(data = filtered_AvgRewN_summary, aes(x = factor(time_factor), y = score_mean, ymin = score_mean - sem, ymax = score_mean + sem), width = 0.05, position = position_nudge(x = 0.2)) +
  labs(
    title = "Avg 'No' Reward Scores by Time Point", 
    y = "Score", 
    x = "Time Point", 
    fill = "Time Point",  # Legend title for fill
    color = "Time Point"  # Legend title for color
  ) +
  theme_minimal() +
  theme(
    legend.position = "right",
    legend.title = element_text(face = "bold"), # Make legend title bold
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels by 45 degrees
  ) +
  ylim(-5, 105)

print(p8)

# Combine raincloud plots and place the legend on the right
combined_plot78 <- p7 + p8 + plot_layout(guides = 'collect') &
  theme(legend.position = 'right')

# Print the combined plot
print(combined_plot78)

### Repeating steps above but stratifying by both time points and epidemiological waves
# Create the summary avg risk 'Y' data frame
filtered_AvgRiskY_waves <- covid_long_final %>%
  group_by(time_factor, covid_group) %>%
  dplyr::summarise(
    score_mean = mean(avg_risk_Y, na.rm = TRUE),
    n = n(), # Sample size for each group
    sem = sd(avg_risk_Y, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

# Create the summary avg risk 'N' data frame
filtered_AvgRiskN_waves <- covid_long_final %>%
  group_by(time_factor, covid_group) %>%
  dplyr::summarise(
    score_mean = mean(avg_risk_N, na.rm = TRUE),
    n = n(), # Sample size for each group
    sem = sd(avg_risk_N, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

# Create the summary avg reward 'Y' data frame
filtered_AvgRewY_waves <- covid_long_final %>%
  group_by(time_factor, covid_group) %>%
  dplyr::summarise(
    score_mean = mean(avg_rew_Y, na.rm = TRUE),
    n = n(), # Sample size for each group
    sem = sd(avg_rew_Y, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

# Create the summary avg reward 'N' data frame
filtered_AvgRewN_waves <- covid_long_final %>%
  group_by(time_factor, covid_group) %>%
  dplyr::summarise(
    score_mean = mean(avg_rew_N, na.rm = TRUE),
    n = n(), # Sample size for each group
    sem = sd(avg_rew_N, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

# Create a avg 'yes' risk raincloud plot
ggplot(covid_long_final, aes(x = time_factor, y = avg_risk_Y, fill = covid_group, color = covid_group)) +
  geom_flat_violin(adjust = 1.5, trim = FALSE, alpha = 0.5, position = position_nudge(x = 0.2, y = 0), colour = NA) +
  geom_point(aes(x = as.numeric(time_factor)-0.25, y = avg_risk_Y, colour = covid_group), position = position_jitter(width = .05), size = .5, shape = 20) +
  geom_boxplot(outlier.shape = NA, alpha = 0.5, width = 0.25, position = position_dodge(width = 0.3), colour = "black") +
  geom_line(data = filtered_AvgRiskY_waves, aes(x = factor(time_factor), y = score_mean, group = covid_group, colour = covid_group), linetype = 2, position = position_nudge(x = 0.2)) +
  geom_point(data = filtered_AvgRiskY_waves, aes(x = factor(time_factor), y = score_mean), shape = 18, position = position_nudge(x = 0.2)) +
  geom_errorbar(data = filtered_AvgRiskY_waves, aes(x = factor(time_factor), y = score_mean, ymin = score_mean - sem, ymax = score_mean + sem), width = 0.05, position = position_nudge(x = 0.2)) +
  labs(
    title = "Avg 'Yes' Risk Scores by Time Point & Wave", 
    y = "Score", 
    x = "Time Point", 
    fill = "COVID Wave",  # Legend title for fill
    color = "COVID Wave"  # Legend title for color
  ) +
  theme_minimal() +
  theme(
    legend.position = "right",
    legend.title = element_text(face = "bold"), # Make legend title bold
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels by 45 degrees
  ) +
  ylim(-5, 105)

# Create a avg 'no' risk raincloud plot
ggplot(covid_long_final, aes(x = time_factor, y = avg_risk_N, fill = covid_group, color = covid_group)) +
  geom_flat_violin(adjust = 1.5, trim = FALSE, alpha = 0.5, position = position_nudge(x = 0.2, y = 0), colour = NA) +
  geom_point(aes(x = as.numeric(time_factor)-0.25, y = avg_risk_N, colour = covid_group), position = position_jitter(width = .05), size = .5, shape = 20) +
  geom_boxplot(outlier.shape = NA, alpha = 0.5, width = 0.25, position = position_dodge(width = 0.3), colour = "black") +
  geom_line(data = filtered_AvgRiskN_waves, aes(x = factor(time_factor), y = score_mean, group = covid_group, colour = covid_group), linetype = 2, position = position_nudge(x = 0.2)) +
  geom_point(data = filtered_AvgRiskN_waves, aes(x = factor(time_factor), y = score_mean), shape = 18, position = position_nudge(x = 0.2)) +
  geom_errorbar(data = filtered_AvgRiskN_waves, aes(x = factor(time_factor), y = score_mean, ymin = score_mean - sem, ymax = score_mean + sem), width = 0.05, position = position_nudge(x = 0.2)) +
  labs(
    title = "Avg 'No' Risk Scores by Time Point & Wave", 
    y = "Score", 
    x = "Time Point", 
    fill = "COVID Wave",  # Legend title for fill
    color = "COVID Wave"  # Legend title for color
  ) +
  theme_minimal() +
  theme(
    legend.position = "right",
    legend.title = element_text(face = "bold"), # Make legend title bold
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels by 45 degrees
  ) +
  ylim(-5, 105)

# Create a avg 'yes' reward raincloud plot
ggplot(covid_long_final, aes(x = time_factor, y = avg_rew_Y, fill = covid_group, color = covid_group)) +
  geom_flat_violin(adjust = 1.5, trim = FALSE, alpha = 0.5, position = position_nudge(x = 0.2, y = 0), colour = NA) +
  geom_point(aes(x = as.numeric(time_factor)-0.25, y = avg_rew_Y, colour = covid_group), position = position_jitter(width = .05), size = .5, shape = 20) +
  geom_boxplot(outlier.shape = NA, alpha = 0.5, width = 0.25, position = position_dodge(width = 0.3), colour = "black") +
  geom_line(data = filtered_AvgRewY_waves, aes(x = factor(time_factor), y = score_mean, group = covid_group, colour = covid_group), linetype = 2, position = position_nudge(x = 0.2)) +
  geom_point(data = filtered_AvgRewY_waves, aes(x = factor(time_factor), y = score_mean), shape = 18, position = position_nudge(x = 0.2)) +
  geom_errorbar(data = filtered_AvgRewY_waves, aes(x = factor(time_factor), y = score_mean, ymin = score_mean - sem, ymax = score_mean + sem), width = 0.05, position = position_nudge(x = 0.2)) +
  labs(
    title = "Avg 'Yes' Reward Scores by Time Point & Wave", 
    y = "Score", 
    x = "Time Point", 
    fill = "COVID Wave",  # Legend title for fill
    color = "COVID Wave"  # Legend title for color
  ) +
  theme_minimal() +
  theme(
    legend.position = "right",
    legend.title = element_text(face = "bold"), # Make legend title bold
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels by 45 degrees
  ) +
  ylim(-5, 105)

# Create a avg 'no' reward raincloud plot
ggplot(covid_long_final, aes(x = time_factor, y = avg_rew_N, fill = covid_group, color = covid_group)) +
  geom_flat_violin(adjust = 1.5, trim = FALSE, alpha = 0.5, position = position_nudge(x = 0.2, y = 0), colour = NA) +
  geom_point(aes(x = as.numeric(time_factor)-0.25, y = avg_rew_N, colour = covid_group), position = position_jitter(width = .05), size = .5, shape = 20) +
  geom_boxplot(outlier.shape = NA, alpha = 0.5, width = 0.25, position = position_dodge(width = 0.3), colour = "black") +
  geom_line(data = filtered_AvgRewN_waves, aes(x = factor(time_factor), y = score_mean, group = covid_group, colour = covid_group), linetype = 2, position = position_nudge(x = 0.2)) +
  geom_point(data = filtered_AvgRewN_waves, aes(x = factor(time_factor), y = score_mean), shape = 18, position = position_nudge(x = 0.2)) +
  geom_errorbar(data = filtered_AvgRewN_waves, aes(x = factor(time_factor), y = score_mean, ymin = score_mean - sem, ymax = score_mean + sem), width = 0.05, position = position_nudge(x = 0.2)) +
  labs(
    title = "Avg 'No' Reward Scores by Time Point & Wave", 
    y = "Score", 
    x = "Time Point", 
    fill = "COVID Wave",  # Legend title for fill
    color = "COVID Wave"  # Legend title for color
  ) +
  theme_minimal() +
  theme(
    legend.position = "right",
    legend.title = element_text(face = "bold"), # Make legend title bold
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels by 45 degrees
  ) +
  ylim(-5, 105)

# Count unique subjects in each category of 'covid_group'
covid_wave_counts <- covid_long_final %>%
  distinct(record_id, covid_group) %>%
  count(covid_group)

# Generate bar plot showing number of subjects in each wave
ggplot(covid_wave_counts, aes(x = covid_group, y = n, fill = covid_group)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), vjust = -0.3, size = 3.5) +  # Add labels above bars
  labs(title = "Count of Subjects per COVID Wave",
       x = "COVID Wave",
       y = "Number of Subjects") +
  theme_minimal() +
  theme(legend.position = "none")  # Remove legend if not needed

# Extract month-year and count distinct subjects
monthly_baseline <- covid_long_final %>%
  distinct(record_id, baseline_date_complete) %>%
  mutate(month_year = format(baseline_date_complete, "%Y-%m")) %>%
  filter(baseline_date_complete >= as.Date("2020-05-01") & baseline_date_complete <= as.Date("2021-02-28")) %>%
  count(month_year)

# Plot the number of subjects completing baseline in each month-year
ggplot(monthly_baseline, aes(x = month_year, y = n, fill = month_year)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), vjust = -0.5, size = 3.5) +  # Adding count labels above the bars
  labs(title = "Monthly Count of Subjects Completing Baseline Session",
       x = "Month-Year",
       y = "Number of Subjects") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for better readability
        legend.position = "none")  # Remove the legend

```

```{r Descriptive Visualizations for Mental Health Data, message=FALSE, warning=FALSE}
# Loop over each unique variable in the 'variable' column
for (variable in unique(mentalhealth_survey_data_long$variable)) {
  # Filter the data for the current variable
  data_filtered <- mentalhealth_survey_data_long %>% 
    filter(variable == !!variable)

  # Assuming you have summary data for each variable stored in a way that can be accessed like this:
  summary_data <- get(paste0("filtered_", variable, "_summary"))

  # Ensure time_factor is ordered correctly
  summary_data$time_factor <- factor(summary_data$time_factor, levels = c(
    "Baseline", "Two Week Follow-Up", "One Month Follow-Up", 
    "Six Week Follow-Up", "Two Month Follow-Up", "Ten Week Follow-Up", 
    "Three Month Follow-Up"
  ))
  
  # Create the plot
  p <- ggplot(data_filtered, aes(x = time_factor, y = value, fill = time_factor, color = time_factor)) +
    geom_flat_violin(aes(fill = time_factor), adjust = 1.5, trim = FALSE, alpha = 0.5, position = position_nudge(x = 0.2, y = 0), colour = NA) +
    geom_point(aes(fill = time_factor, color = time_factor), position = position_jitter(width = .05), size = .5, shape = 20) +
    geom_boxplot(aes(fill = time_factor, colour = time_factor), outlier.shape = NA, alpha = 0.5, width = 0.15, position = position_nudge(x = -0.2, y = 0), colour = "black") +
    geom_point(data = summary_data, aes(x = factor(time_factor), y = score_mean, fill = time_factor, color = time_factor), shape = 18, position = position_nudge(x = 0.2)) +
    geom_errorbar(data = summary_data, aes(x = factor(time_factor), y = score_mean, ymin = score_mean - sem, ymax = score_mean + sem, fill = time_factor, colour = time_factor), width = 0.05, position = position_nudge(x = 0.2)) +
    geom_line(data = summary_data, aes(x = factor(time_factor), y = score_mean), group = 1, colour = "black", size = 0.5, linetype = "dashed", position = position_nudge(x = 0.2)) +  # modified line
    labs(
      title = paste(variable, "Scores by Time Point"), 
      y = "Score", 
      x = "Time Point", 
      fill = "Time Point",  # Legend title for fill
      color = "Time Point"  # Legend title for color
    ) +
    theme_minimal() +
    theme(
      legend.position = "right",
      legend.title = element_text(face = "bold"), # Make legend title bold
      axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels by 45 degrees
    )

  # Print the plot
  print(p)
}

```

## Behavioral Computations: Multilevel Modeling & Visualizations

Random intercept models are established to analyze various behavioral, risk, and reward metrics. Results are displayed in formatted tables that highlight both fixed and random effects across different behavior sums and averages.

```{r Random Intercept Models, message=FALSE, warning=FALSE}
# Rename 'record_id' to 'id' in the dataframe 'covid_long_final'
covid_long_final <- covid_long_final %>%
  dplyr::rename(id = record_id)

# Random intercept models
model_random_intercept_num_beh_Y_sum <- lmer(yes_counts ~ time + (1|id), data = covid_long_final)
model_random_intercept_num_beh_N_sum <- lmer(no_counts ~ time + (1|id), data = covid_long_final)
model_random_intercept_avg_risk_Y <- lmer(avg_risk_Y ~ time + (1|id), data = covid_long_final)
model_random_intercept_avg_risk_N <- lmer(avg_risk_N ~ time + (1|id), data = covid_long_final)
model_random_intercept_avg_rew_Y <- lmer(avg_rew_Y ~ time + (1|id), data = covid_long_final)
model_random_intercept_avg_rew_N <- lmer(avg_rew_N ~ time + (1|id), data = covid_long_final)

model_random_intercept_avg_low_risk_Y <- lmer(avg_low_risk_Y ~ time + (1|id), data = covid_long_final)
model_random_intercept_avg_low_risk_N <- lmer(avg_low_risk_N ~ time + (1|id), data = covid_long_final)
model_random_intercept_avg_low_rew_Y <- lmer(avg_low_rew_Y ~ time + (1|id), data = covid_long_final)
model_random_intercept_avg_low_rew_N <- lmer(avg_low_rew_N ~ time + (1|id), data = covid_long_final)

model_random_intercept_avg_moderate_risk_Y <- lmer(avg_moderate_risk_Y ~ time + (1|id), data = covid_long_final)
model_random_intercept_avg_moderate_risk_N <- lmer(avg_moderate_risk_N ~ time + (1|id), data = covid_long_final)
model_random_intercept_avg_moderate_rew_Y <- lmer(avg_moderate_rew_Y ~ time + (1|id), data = covid_long_final)
model_random_intercept_avg_moderate_rew_N <- lmer(avg_moderate_rew_N ~ time + (1|id), data = covid_long_final)

model_random_intercept_avg_high_risk_Y <- lmer(avg_high_risk_Y ~ time + (1|id), data = covid_long_final)
model_random_intercept_avg_high_risk_N <- lmer(avg_high_risk_N ~ time + (1|id), data = covid_long_final)
model_random_intercept_avg_high_rew_Y <- lmer(avg_high_rew_Y ~ time + (1|id), data = covid_long_final)
model_random_intercept_avg_high_rew_N <- lmer(avg_high_rew_N ~ time + (1|id), data = covid_long_final)

# Creating a grouped table with formatted layout including all models
tab_model(
  title = "Random Intercept Model Results - Risk/Reward Behavior Sums & Averages",
  model_random_intercept_num_beh_Y_sum,
  model_random_intercept_num_beh_N_sum,
  model_random_intercept_avg_risk_Y,
  model_random_intercept_avg_risk_N,
  model_random_intercept_avg_rew_Y,
  model_random_intercept_avg_rew_N,
  model_random_intercept_avg_low_risk_Y,
  model_random_intercept_avg_low_risk_N,
  model_random_intercept_avg_low_rew_Y,
  model_random_intercept_avg_low_rew_N,
  model_random_intercept_avg_moderate_risk_Y,
  model_random_intercept_avg_moderate_risk_N,
  model_random_intercept_avg_moderate_rew_Y,
  model_random_intercept_avg_moderate_rew_N,
  model_random_intercept_avg_high_risk_Y,
  model_random_intercept_avg_high_risk_N,
  model_random_intercept_avg_high_rew_Y,
  model_random_intercept_avg_high_rew_N
)

```

Linear and quadratic growth models are fitted to explore longitudinal trajectories and capture curvature in time trends of the dataset, incorporating both fixed effects of time and random effects of individual trajectories. The outcomes of these models are presented in structured tables.

```{r Linear Growth Model Fitting, message=FALSE, warning=FALSE}
# Fit linear growth model with random intercepts and slopes and homoscedastic level-1 residuals
model_random_slope_num_beh_Y_sum <- lmer(yes_counts ~ time + (1 + time|id), data = covid_long_final, REML = FALSE, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
model_random_slope_num_beh_N_sum <- lmer(no_counts ~ time + (1 + time|id), data = covid_long_final, REML = FALSE, control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
model_random_slope_avg_risk_Y <- lmer(avg_risk_Y ~ time + (1 + time|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_random_slope_avg_risk_N <- lmer(avg_risk_N ~ time + (1 + time|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_random_slope_avg_rew_Y <- lmer(avg_rew_Y ~ time + (1 + time|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_random_slope_avg_rew_N <- lmer(avg_rew_N ~ time + (1 + time|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))

model_random_slope_avg_low_risk_Y <- lmer(avg_low_risk_Y ~ time + (1 + time|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_random_slope_avg_low_risk_N <- lmer(avg_low_risk_N ~ time + (1 + time|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_random_slope_avg_low_rew_Y <- lmer(avg_low_rew_Y ~ time + (1 + time|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_random_slope_avg_low_rew_N <- lmer(avg_low_rew_N ~ time + (1 + time|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))

model_random_slope_avg_moderate_risk_Y <- lmer(avg_moderate_risk_Y ~ time + (1 + time|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_random_slope_avg_moderate_risk_N <- lmer(avg_moderate_risk_N ~ time + (1 + time|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_random_slope_avg_moderate_rew_Y <- lmer(avg_moderate_rew_Y ~ time + (1 + time|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_random_slope_avg_moderate_rew_N <- lmer(avg_moderate_rew_N ~ time + (1 + time|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))

model_random_slope_avg_high_risk_Y <- lmer(avg_high_risk_Y ~ time + (1 + time|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_random_slope_avg_high_risk_N <- lmer(avg_high_risk_N ~ time + (1 + time|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_random_slope_avg_high_rew_Y <- lmer(avg_high_rew_Y ~ time + (1 + time|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_random_slope_avg_high_rew_N <- lmer(avg_high_rew_N ~ time + (1 + time|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))

# Creating a grouped table with formatted layout including all models
tab_model(
  title = "Random Linear Growth Model Results - Risk/Reward Behavior Sums & Averages",
  model_random_slope_num_beh_Y_sum,
  model_random_slope_num_beh_N_sum,
  model_random_slope_avg_risk_Y,
  model_random_slope_avg_risk_N,
  model_random_slope_avg_rew_Y,
  model_random_slope_avg_rew_N,
  model_random_slope_avg_low_risk_Y,
  model_random_slope_avg_low_risk_N,
  model_random_slope_avg_low_rew_Y,
  model_random_slope_avg_low_rew_N,
  model_random_slope_avg_moderate_risk_Y,
  model_random_slope_avg_moderate_risk_N,
  model_random_slope_avg_moderate_rew_Y,
  model_random_slope_avg_moderate_rew_N,
  model_random_slope_avg_high_risk_Y,
  model_random_slope_avg_high_risk_N,
  model_random_slope_avg_high_rew_Y,
  model_random_slope_avg_high_rew_N
)

```

```{r Quadratic Growth Model Fitting, message=FALSE, warning=FALSE}
# Quadratic model with random intercept and random slope
model_quad_num_beh_Y_sum <- lmer(yes_counts ~ time + I(time^2) + (1 + time + I(time^2)|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun= 2e5)))
model_quad_num_beh_N_sum <- lmer(no_counts ~ time + I(time^2) + (1 + time + I(time^2)|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun= 2e5)))
model_quad_avg_risk_Y <- lmer(avg_risk_Y ~ time + I(time^2) + (1 + time + I(time^2)|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))
model_quad_avg_risk_N <- lmer(avg_risk_N ~ time + I(time^2) + (1 + time + I(time^2)|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))
model_quad_avg_rew_Y <- lmer(avg_rew_Y ~ time + I(time^2) + (1 + time + I(time^2)|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))
model_quad_avg_rew_N <- lmer(avg_rew_N ~ time + I(time^2) + (1 + time + I(time^2)|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

model_quad_avg_low_risk_Y <- lmer(avg_low_risk_Y ~ time + I(time^2) + (1 + time + I(time^2)|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_quad_avg_low_risk_N <- lmer(avg_low_risk_N ~ time + I(time^2) + (1 + time + I(time^2)|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_quad_avg_low_rew_Y <- lmer(avg_low_rew_Y ~ time + I(time^2) + (1 + time + I(time^2)|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_quad_avg_low_rew_N <- lmer(avg_low_rew_N ~ time + I(time^2) + (1 + time + I(time^2)|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))

model_quad_avg_moderate_risk_Y <- lmer(avg_moderate_risk_Y ~ time + I(time^2) + (1 + time + I(time^2)|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_quad_avg_moderate_risk_N <- lmer(avg_moderate_risk_N ~ time + I(time^2) + (1 + time + I(time^2)|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_quad_avg_moderate_rew_Y <- lmer(avg_moderate_rew_Y ~ time + I(time^2) + (1 + time + I(time^2)|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_quad_avg_moderate_rew_N <- lmer(avg_moderate_rew_N ~ time + I(time^2) + (1 + time + I(time^2)|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))

model_quad_avg_high_risk_Y <- lmer(avg_high_risk_Y ~ time + I(time^2) + (1 + time + I(time^2)|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_quad_avg_high_risk_N <- lmer(avg_high_risk_N ~ time + I(time^2) + (1 + time + I(time^2)|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_quad_avg_high_rew_Y <- lmer(avg_high_rew_Y ~ time + I(time^2) + (1 + time + I(time^2)|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))
model_quad_avg_high_rew_N <- lmer(avg_high_rew_N ~ time + I(time^2) + (1 + time + I(time^2)|id), data = covid_long_final, REML = FALSE, control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 2e5)))

# Creating a grouped table with formatted layout including all models
tab_model(
  title = "Random Quadratic Growth Model Results - Risk/Reward Behavior Sums & Averages",
  model_quad_num_beh_Y_sum,
  model_quad_num_beh_N_sum,
  model_quad_avg_risk_Y,
  model_quad_avg_risk_N,
  model_quad_avg_rew_Y,
  model_quad_avg_rew_N,
  model_quad_avg_low_risk_Y,
  model_quad_avg_low_risk_N,
  model_quad_avg_low_rew_Y,
  model_quad_avg_low_rew_N,
  model_quad_avg_moderate_risk_Y,
  model_quad_avg_moderate_risk_N,
  model_quad_avg_moderate_rew_Y,
  model_quad_avg_moderate_rew_N,
  model_quad_avg_high_risk_Y,
  model_quad_avg_high_risk_N,
  model_quad_avg_high_rew_Y,
  model_quad_avg_high_rew_N
)

```

Finally, visualizations of the predicted trajectories from these models are generated, using polynomial regression lines to depict dynamic changes and individual variability over time.

```{r Model Visualizations, message=FALSE, warning=FALSE}
# Plot model implied trajectories, quadratic
ggplot(covid_long_final,aes(time,predict(model_quad_num_beh_Y_sum))) +
  ylim(0, 40) +
  geom_smooth(aes(group=id),method='lm',formula=y~x+I(x^2),se=FALSE,
              color="black",size=.1) +
  labs(x = "Time Point") +
  labs(y = "Predicted Sum Number of 'Yes' Behaviors")

ggplot(covid_long_final,aes(time,predict(model_quad_num_beh_N_sum))) +
  ylim(0, 40) +
  geom_smooth(aes(group=id),method='lm',formula=y~x+I(x^2),se=FALSE,
              color="black",size=.1) +
  labs(x = "Time Point") +
  labs(y = "Predicted Sum Number of 'No' Behaviors")

# Plot model implied trajectories, linear
ggplot(covid_long_final, aes(x = time, y = predict(model_random_slope_num_beh_Y_sum))) +
  geom_smooth(aes(group = id), method = 'lm', formula = y ~ x, se = FALSE, color = "black", size = .1) +
  labs(x = "Time Point", y = "Predicted Sum Number of 'Yes' Behaviors") +
  ylim(0, 40)

ggplot(covid_long_final, aes(x = time, y = predict(model_random_slope_num_beh_N_sum))) +
  geom_smooth(aes(group = id), method = 'lm', formula = y ~ x, se = FALSE, color = "black", size = .1) +
  labs(x = "Time Point", y = "Predicted Sum Number of 'No' Behaviors") +
  ylim(0, 40)

### Imputation code--needed as the predicted values has fewer rows than the original data frame
# Calculate predictions for each model
quad_predicted_avg_risk_Y <- predict(model_quad_avg_risk_Y, re.form = NA)
quad_predicted_avg_risk_N <- predict(model_quad_avg_risk_N, re.form = NA)
quad_predicted_avg_rew_Y <- predict(model_quad_avg_rew_Y, re.form = NA)
quad_predicted_avg_rew_N <- predict(model_quad_avg_rew_N, re.form = NA)
lin_predicted_avg_risk_Y <- predict(model_random_slope_avg_risk_Y, re.form = NA)
lin_predicted_avg_risk_N <- predict(model_random_slope_avg_risk_N, re.form = NA)
lin_predicted_avg_rew_Y <- predict(model_random_slope_avg_rew_Y, re.form = NA)
lin_predicted_avg_rew_N <- predict(model_random_slope_avg_rew_N, re.form = NA)

# Add predicted values to the dataframe, initializing with NA
covid_long_final$quad_predicted_avg_risk_Y <- NA
covid_long_final$quad_predicted_avg_risk_N <- NA
covid_long_final$quad_predicted_avg_rew_Y <- NA
covid_long_final$quad_predicted_avg_rew_N <- NA
covid_long_final$lin_predicted_avg_risk_Y <- NA
covid_long_final$lin_predicted_avg_risk_N <- NA
covid_long_final$lin_predicted_avg_rew_Y <- NA
covid_long_final$lin_predicted_avg_rew_N <- NA

# Fill in the predicted values where available
covid_long_final$quad_predicted_avg_risk_Y[!is.na(quad_predicted_avg_risk_Y)] <- quad_predicted_avg_risk_Y
covid_long_final$quad_predicted_avg_risk_N[!is.na(quad_predicted_avg_risk_N)] <- quad_predicted_avg_risk_N
covid_long_final$quad_predicted_avg_rew_Y[!is.na(quad_predicted_avg_rew_Y)] <- quad_predicted_avg_rew_Y
covid_long_final$quad_predicted_avg_rew_N[!is.na(quad_predicted_avg_rew_N)] <- quad_predicted_avg_rew_N
covid_long_final$lin_predicted_avg_risk_Y[!is.na(lin_predicted_avg_risk_Y)] <- lin_predicted_avg_risk_Y
covid_long_final$lin_predicted_avg_risk_N[!is.na(lin_predicted_avg_risk_N)] <- lin_predicted_avg_risk_N
covid_long_final$lin_predicted_avg_rew_Y[!is.na(lin_predicted_avg_rew_Y)] <- lin_predicted_avg_rew_Y
covid_long_final$lin_predicted_avg_rew_N[!is.na(lin_predicted_avg_rew_N)] <- lin_predicted_avg_rew_N

# Handle NA predicted values by assigning the mean of the available predictions
quad_mean_predicted_risk_Y <- mean(quad_predicted_avg_risk_Y, na.rm = TRUE)
quad_mean_predicted_risk_N <- mean(quad_predicted_avg_risk_N, na.rm = TRUE)
quad_mean_predicted_rew_Y <- mean(quad_predicted_avg_rew_Y, na.rm = TRUE)
quad_mean_predicted_rew_N <- mean(quad_predicted_avg_rew_N, na.rm = TRUE)
lin_mean_predicted_risk_Y <- mean(lin_predicted_avg_risk_Y, na.rm = TRUE)
lin_mean_predicted_risk_N <- mean(lin_predicted_avg_risk_N, na.rm = TRUE)
lin_mean_predicted_rew_Y <- mean(lin_predicted_avg_rew_Y, na.rm = TRUE)
lin_mean_predicted_rew_N <- mean(lin_predicted_avg_rew_N, na.rm = TRUE)

covid_long_final$quad_predicted_avg_risk_Y[is.na(covid_long_final$quad_predicted_avg_risk_Y)] <- quad_mean_predicted_risk_Y
covid_long_final$quad_predicted_avg_risk_N[is.na(covid_long_final$quad_predicted_avg_risk_N)] <- quad_mean_predicted_risk_N
covid_long_final$quad_predicted_avg_rew_Y[is.na(covid_long_final$quad_predicted_avg_rew_Y)] <- quad_mean_predicted_rew_Y
covid_long_final$quad_predicted_avg_rew_N[is.na(covid_long_final$quad_predicted_avg_rew_N)] <- quad_mean_predicted_rew_N
covid_long_final$lin_predicted_avg_risk_Y[is.na(covid_long_final$lin_predicted_avg_risk_Y)] <- lin_mean_predicted_risk_Y
covid_long_final$lin_predicted_avg_risk_N[is.na(covid_long_final$lin_predicted_avg_risk_N)] <- lin_mean_predicted_risk_N
covid_long_final$lin_predicted_avg_rew_Y[is.na(covid_long_final$lin_predicted_avg_rew_Y)] <- lin_mean_predicted_rew_Y
covid_long_final$lin_predicted_avg_rew_N[is.na(covid_long_final$lin_predicted_avg_rew_N)] <- lin_mean_predicted_rew_N

# Plotting all four graphs, quadratic
q1 <- ggplot(covid_long_final, aes(x = time, y = quad_predicted_avg_risk_Y)) +
  geom_smooth(aes(group = id), method = 'lm', formula = y ~ x + I(x^2), se = FALSE, color = "black", size = .1) +
  labs(x = "Time Point", y = "Predicted Average 'Yes' Risk Score")

q2 <- ggplot(covid_long_final, aes(x = time, y = quad_predicted_avg_risk_N)) +
  geom_smooth(aes(group = id), method = 'lm', formula = y ~ x + I(x^2), se = FALSE, color = "black", size = .1) +
  labs(x = "Time Point", y = "Predicted Average 'No' Risk Score")

q3 <- ggplot(covid_long_final, aes(x = time, y = quad_predicted_avg_rew_Y)) +
  geom_smooth(aes(group = id), method = 'lm', formula = y ~ x + I(x^2), se = FALSE, color = "black", size = .1) +
  labs(x = "Time Point", y = "Predicted Average 'Yes' Reward Score")

q4 <- ggplot(covid_long_final, aes(x = time, y = quad_predicted_avg_rew_N)) +
  geom_smooth(aes(group = id), method = 'lm', formula = y ~ x + I(x^2), se = FALSE, color = "black", size = .1) +
  labs(x = "Time Point", y = "Predicted Average 'No' Reward Score")

# Combine and display the plots
grid.arrange(q1, q2, ncol = 2)
grid.arrange(q3, q4, ncol = 2)

# Plotting all four graphs, linear
l1 <- ggplot(covid_long_final, aes(x = time, y = lin_predicted_avg_risk_Y)) +
  geom_smooth(aes(group = id), method = 'lm', formula = y ~ x, se = FALSE, color = "black", size = .1) +
  labs(x = "Time Point", y = "Predicted Average 'Yes' Risk Score")

l2 <- ggplot(covid_long_final, aes(x = time, y = lin_predicted_avg_risk_N)) +
  geom_smooth(aes(group = id), method = 'lm', formula = y ~ x, se = FALSE, color = "black", size = .1) +
  labs(x = "Time Point", y = "Predicted Average 'No' Risk Score")

l3 <- ggplot(covid_long_final, aes(x = time, y = lin_predicted_avg_rew_Y)) +
  geom_smooth(aes(group = id), method = 'lm', formula = y ~ x, se = FALSE, color = "black", size = .1) +
  labs(x = "Time Point", y = "Predicted Average 'Yes' Reward Score")

l4 <- ggplot(covid_long_final, aes(x = time, y = lin_predicted_avg_rew_N)) +
  geom_smooth(aes(group = id), method = 'lm', formula = y ~ x, se = FALSE, color = "black", size = .1) +
  labs(x = "Time Point", y = "Predicted Average 'No' Reward Score")

# Combine and display the plots
grid.arrange(l1, l2, ncol = 2)
grid.arrange(l3, l4, ncol = 2)

```

## Session Information

To enhance **reproducibility**, details about the **working environment** used for these analyses can be found below.

```{r}
sessionInfo()
```
